---
title: "Ensemble Clustering"
author: "mwinkler"
date: "September 30, 2016"
output: html_document
---

```{r}
setwd('/Users/mwinkler/Documents/coursework/advanced_data_mining/')
cities <- read.csv("cities10k.csv")
head(cities)
```

Extract lat & long from the dataset:

```{r}
loc <- cities[, 6:7]
plot(loc$Longitude, loc$Latitude, pch = 20, cex=.1)
```

Create 2 K-means partiitions and plot again:

```{r}
set.seed(1234)
clust.k02 <- kmeans(loc, 2)
plot(loc$Longitude, loc$Latitude, pch = 20, cex=.1, col = clust.k02$cluster)
```

5 partitions:

```{r}
set.seed(1234)
clust.k05 <- kmeans(loc, 5)
plot(loc$Longitude, loc$Latitude, pch = 20, cex=.1, col = clust.k05$cluster)
```

10 partitions:

```{r}
set.seed(1234)
clust.k10 <- kmeans(loc, 10)
plot(loc$Longitude, loc$Latitude, pch = 20, cex=.1, col = clust.k10$cluster)
```

25 partitions:

```{r}
set.seed(1234)
clust.k25 <- kmeans(loc, 25)
plot(loc$Longitude, loc$Latitude, pch = 20, cex=.1, col = clust.k25$cluster)
```

25 partitions with a different seed:

```{r}
set.seed(2345)
clust.k25.2 <- kmeans(loc, 25)
plot(loc$Longitude, loc$Latitude, pch = 20, cex=.1, col = clust.k25.2$cluster)
```

25 partitions with yet a different seed:

```{r}
set.seed(3456)
clust.k25.2 <- kmeans(loc, 25)
plot(loc$Longitude, loc$Latitude, pch = 20, cex=.1, col = clust.k25.2$cluster)
```

### Using "clue" for ensemble clustering:

```{r}
# install.packages("clue") -- not run
library(clue)
help(cl_boot)
```


Create the partitions:

```{r}
set.seed(3456)
ensemble <- cl_boot(loc, 50, 25)
ensemble
```

Look at agreement between partitionings:

```{r}
cl_agreement(ensemble)
```

Aggregate results from 50 partitionings into a single one using a soft consensus approach:

```{r}
consensus.se <- cl_consensus(ensemble, method = "SE", control = list(k = 25))
help("cl_consensus")
consensus.se$.Data[1,]

?cl_consensus
```

Aggregate again using a hard consensus:

```{r}
consensus.he <- cl_consensus(ensemble, method = "HE", control = list(k = 25))
consensus.he$.Data[1, ]
```

Produce a new set of assignments from the hard consensus, and replot:

```{r}
assignments <- cl_class_ids(consensus.he)
plot(loc$Longitude, loc$Latitude, pch = 20, cex = .1, col = assignments)
```
